Should geophysicists use the gravity disturbance or the anomaly?

### 2018-05-29 manuscript/letter.tex
Add Zenodo DOI to README and text
Included a link to the DOI and Github repository in the paper
acknowledgements section.

%Extra packages
\usepackage{graphicx}
\usepackage{amsmath}

@@

\author[Hallam et al.]{
\parbox{\linewidth}{%
    Vanderlei C. Oliveira Jr$^1$\thanks{Email: vanderlei@on.br},
    Leonardo Uieda$^2$, Val\'{e}ria C. F. Barbosa$^1$, and
    \linebreak Kristoffer A. T. Hallam$^{1}$ 
    \vspace{0.3cm}
}%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

@@

\begin{acknowledgments}
The authors would like to thank the editor and all the
reviewers for their criticisms and corrections.
\end{acknowledgments}

>>>>

%Extra packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
    allcolors=black,
}

@@

\author[Oliveira Jr et al.]{
\parbox{\linewidth}{%
    Vanderlei C. Oliveira Jr$^1$\thanks{Email: vanderlei@on.br},
    Leonardo Uieda$^2$, Val\'{e}ria C. F. Barbosa$^1$, and
    \linebreak Kristoffer A. T. Hallam$^{1}$
    \vspace{0.3cm}
}%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

@@

\begin{acknowledgments}
The authors would like to thank the editor and reviewers for their criticisms
and corrections.
All source code and data used to generate the results presented here are
available at
\href{https://doi.org/10.5281/zenodo.1255306}{doi.org/10.5281/zenodo.1255306}
and
\href{https://github.com/pinga-lab/use-the-disturbance}{github.com/pinga-lab/use-the-disturbance}.
\end{acknowledgments}
